---
title: 'Title'
author: 'John Doe'
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  unilur::tutorial_html_solution: default
---

```{r, echo=FALSE}
#(1) without solution: use
#unilur::tutorial_html: default

#(2) with solution: use
#unilur::tutorial_html_solution: default
  
library(knitr)

knitr::opts_template$set(alert = list(box.title = "Watch out!", box.body = list(fill = "#fa5b42", colour = "#fdf6d4"), box.collapse = TRUE, box.icon = "fa-exclamation-triangle"))
```

You can write some text appearing in both files using the standard [markup language](http://rmarkdown.rstudio.com).

Use the `r` chunk to display some code in both files.

```{r}
head(cars)
```

Use the `r` chunk with `solution = TRUE` to display and evaluate the chunk only in the solution file.

```{r, solution = TRUE}
# Only visible and evaluated in the solution file...
plot(cars)
```

You can also add some markdown formatted text with the asis engine together with `solution = TRUE`

```{block, solution = TRUE}
This is the text explaining how to obtain the solution and written in **Rmarkdown**
```

Use the knit dropdown menu on the knit button to generate the desired output:

- Using `unilur::tutorial_pdf_solution` or `unilur::tutorial_html_solution` will show the solution boxes.
- Using `unilur::tutorial_pdf` or `unilur::tutorial_html` will hide them from the output.

```{block, box.title = "Tip", box.body = list(fill = "lightblue")}
You can also include custom boxes to highlight some content. Read the [article](http://koncina.github.io/unilur/articles/custom-boxes.html) to learn more about how to customize the appearance.
```

